working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-08 Manuscript_draft/Manuscript_draft.Rmd
Calculate compatibility or leave as selfing rate

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
load("myEnv.RData")
library(nlme)
library(lme4)
library(ggplot2)
Model.2 <- lmer(hp_effect ~ compatibility + (1 | Focal), data = ALL)
ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(Model.2))))
